Smart Model Elimination for Efficient Automated Machine Learning in Healthcare

### 2024-06-25 paper/paper.tex
update emails
new citations

\author{%
  Eric Su Zhang$^1$ \\
  St. Mark's School of Texas\\
  10600 Preston Rd, Dallas, TX 75230\\
  \texttt{ericspring08@gmail.com} \\
  % examples of more authors
  \And
  Benjamin Joseph Michael Standefer$^2$ \\
  St. Mark's School of Texas \\
  10600 Preston Rd, Dallas, TX 75230 \\
  \texttt{bjmstandefer@gmail.com} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\begin{abstract}
  Automated Machine Learning or AutoML has emerged as a popular field of research. We performed a literature review of existing AutoML papers and conducted a survey on five popular AutoML frameworks. Many of these frameworks optimize a form of model selection, but they all require every model to be run and evaluated. We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant. SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" brute-force model, but in a fraction of the time. We also believe this innovation is particularly relevant to machine learning in healthcare because of the necessity for efficient diesease prediction. 
\end{abstract}

@@

Machine learning (ML) is a type of artificial intelligence (AI) that uses searching and trend-determining to make predictions. ML algorithms are trained and tested on a given dataset to become "smarter". Once they've learned the patterns typical of that data, they can make predictions based on similar data. These algorithms also require additional processes, however, like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning. This makes the process complex and time-inefficient. To do this on a larger scale and at greater speeds, recent research and effort have been put into Auto ML frameworks [1].

One sector of the global industry that has the most potential for beneficial integration of AutoML frameworks is healthcare, particularly in developing countries. These countries have severe shortages of healthcare workers and limited tools for diagnosis. For example, Africa has 2.3 healthcare workers per 1000 individuals, while the Americas have 24.8 healthcare workers per 1000 [2]. The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030 [3]. Medical AI's typically automate repetitive tasks, making time consumption a primary concern [4]. This coupled with a lack of adequate resources makes designing faster diagnostic systems for developing countries' medical sectors a pivotal issue. 
%
Most AutoML frameworks implement some form of model selection where a pool of models are filtered until a final model is selected. However, these frameworks require that every model to be run to filter out [1]. In theory, this means that much energy is spent training models that are unlikely to be selected. We propose SMEML, a novel model selection algorithm that automatically eliminates models that it believes will not be performant.

@@

\begin{table}
  \caption{Survey of Existing AutoML Frameworks}
  \label{automl-survey}
  \centering
  \begin{tabular}{lllllllll}
    \toprule
    Framework & EOU & M & FE & TM & HPT & Inter & Custom\\
    \midrule
    H2O AutoML & Easy & 12 & Basic & Yes & Auto & SHAP & High\\
    TPOT & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
    MLJAR & Easy & 12 & Advanced & Yes & Auto & Basic & High\\
    FLAML & Easy & 9 & Limited & Yes & Auto & SHAP & Low-Moderate\\
    LightAutoML & Easy & 11 & Advanced & Yes & Auto & Basic & Moderate\\
    \bottomrule
  \end{tabular}
  \captionsetup{font=footnotesize}
  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, M: \# of models evaluated by framework, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
\end{table}
We systematically reviewed and compared five different AutoML frameworks, comparing every feature relevant to medical implementation [5-10]. Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.

@@

Keeping the factors we have laid out in mind, we also uncovered a key continuity in framework design: frameworks must run the majority of their models to maximize accuracy at the expense of efficiency. Given the restricted nature of tabular data, there are some models that are less likely to perform well, thus running and training these models is wasteful. Cutting these models completely, however, is not optimal, as they are the best option in a minority of cases. We hypothesized that using a combination of layered machine learning implementation and meta-feature extraction would yield an equally versatile system that minimizes time spent on prediction while still maximizing the other quantities.

\section{Methodology}
When considering a specific dataset, the distribution and relationship between datapoints can give us clues as to which models are likely to perform best. For example, linear models tend to work better on datasets where there is a linear relationship between features [11]. Accordingly, we can develop a boosting model to predict the best models based off extracted attributes from a dataset. These extracted attributes are shown in Table 2. Each attribute attempts to capture a specific type of relationship or distribution within the data. The variable importance of each attribute is shown in the "Weight" column. Linearity and data distribution are the most important attributes in determining the best model.

We considered 28 different models, including all supervised and semi-supervised sklearn classification models and common boosting models such as XGBoost, Lightgbm, and Catboost.

To implement this model elimination process, we trained a boosting model on 268 kaggle datasets. We chose medical datasets and focused our approach on binary classification. We extracted the attributes in Table 2 from each dataset: this is the input for the boosting model. We then ran a "dumb" framework that trained every model on each dataset. The accuracy of every model is ranked and every model is treated as a label with its value being its rank. Then we trained a multilabel regression to predict the rank of each model, giving the extracted attributes. We produced a median spearman correlation of 0.7301 between the predicted rank and the actual rank and a median p-value of 1.032e-05. Furthermore, we guarantee that we can predict a top two model within the predicted top eight 90.12\% of the time.

When a user inputs a dataset into SMEML, it first extracts the attributes from the dataset. It feeds these attributes into the boosting model to get the predicted rank of each model. Since we have determined that we can predict a top two model within the predicted top eight quite confidently, we can eliminate the bottom 18 models from the list. We run Bayseian optimization on the top eight models to get the best hyperparamters for each model. We select the top models that have significantly better performance than other models. These models are stacked together to form the final model. This process is shown in Figure 1.
\begin{table}
  \caption{Attributes extracted from a dataset}
  \label{model-options-table}
  \centering
  \begin{tabular}{llll}
    \toprule
    Attribute & Formula & Purpose & Weight\\
    \midrule
    \# of Rows & $|\mathbf{A}|_r$ & DS & .0422 \\
    \hline
    \# of Columns & $|\mathbf{A}|_c$ & DS & .0415 \\
    \hline
    Target Distribution &
    $\frac{\max(\text{count}_1, \text{count}_0)}{|\mathbf{A}|_r}$
    & DT & .0489 \\
    \hline
    Numerical Columns &
    $\frac{|\mathbf{A}_{num}|}{|\mathbf{A}|_{c}}$
    & DT & .0428 \\
    \hline
    Binary Categorical Columns &
    $\frac{|\mathbf{A}_{bin}|}{|\mathbf{A}|_{c}}$
    & DT & .0117 \\
    \hline
    Mean \# of Distinct Values  & $\mu \left\{\text{\# of distinct values in column}\right\}$ & DT & .0076 \\ 
    \hline
    Mean IQR  & $\mu \left\{\text{IQR of column}\right\}$ & DD & .0594 \\ 
    \hline
    STD of IQR  & $\sigma \left\{\text{IQR of column}\right\}$ & DD & .0700 \\
    \hline
    Mean Q1 & $\mu \left\{\text{Q1 of column}\right\}$ & DD & .0789 \\
    \hline
    STD of Q1  & $\sigma \left\{\text{Q1 of column}\right\}$ & DD & .0613 \\
    \hline
    Mean Q3  & $\mu \left\{\text{Q3 of column}\right\}$ & DD & .0812 \\
    \hline
    STD of Q3  & $\sigma \left\{\text{Q3 of column}\right\}$ & DD & .1103 \\
    \hline
    Mean Percent of Z-Score Outliers  & 
    $\mu \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & ODP & .0558 \\
    \hline
    STD of Percent of Z-Score Outliers  &
    $\sigma \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & ODP & .0798 \\
    \hline
    Mean Correlation& $\mu \left\{\text{Correlation Matrix}\right\}$ & DL & .0559 \\
    \hline
    STD of Correlation & $\sigma \left\{\text{Correlation Matrix}\right\}$ & DL & .1526 \\
    \bottomrule
  \end{tabular}
  \captionsetup{font=footnotesize}
  \caption*{\textbf{Abbreviations}: DS: Data Size, DT: Data Type, DD: Data Distribution, ODP: Outlier Data Points, DL: Data Linearity}
\end{table}

\begin {figure}
\centering
\includegraphics[width=\textwidth]{smeml-flowchart.png}
\caption{SMEML Process}
\end{figure}

@@

\subsection{Results}
\begin{table}
  \caption{Experiment Results}
  \label{model-options-table}
  \centering
  \begin{tabular}{llllll}
    \toprule
    % group 2, 3 as multicolumn and 4, 5 as multicolumn
    Dataset & \multicolumn{2}{c}{Accuracy} & \multicolumn{2}{c}{Time to Train (sec)} & Size (RxC)\\
    \cmidrule(lr){2-3} \cmidrule(lr){4-5}
    & SMEML & Dumb & SMEML & Dumb \\
    \midrule
    Lung Cancer Prediction [12] & .9839 & .9839 & 143.07 & 317.04 & 309x16\\
    Chronic Kidney Disease Dataset [13] & 1.0 & 1.0 & 419.64 & 788.46 & 400x26\\
    Pima Indians Diabetes Dataset [14] & .7857 & .8052 & 161.99 & 374.01 & 768x8 \\
    Brain Stroke Prediction Dataset [15] & .9458 & .9458 & 114.16 & 370.95 & 4892x11\\
    Stroke Prediction Dataset [16] & .9393 & .9393 & 172.67 & 385.23 & 5110x12 \\
    Eye State Classification [17] & .9536 & .9549 & 312.57 & 696.51 & 14980x15\\ 
    \bottomrule
  \end{tabular}
\end{table}

Several observations were made from running these datasets. First, accuracy did not change for 4 of the 6 benchmarks. The other two benchmarks on eye states and diabetes prediction represented a loss of accuracy for SMEML by 0.13\% and 1.95\%, respectively. Training time, however, favored SMEML in every trial. SMEML outperformed the dummy framework by 173.96 seconds in its worst performance on the lung cancer trial and by 383.94 seconds in its best performance on the eye state dataset. Relative to the dummy's performance, a percent decrease in time to run for SMEML of at least 46.78\% could be seen, with a decrease of up to 69.22\% observerd as well. SMEML's worst performance by percent decrease was also the performance in which it returned perfect accuracy. 
\section{Discussion}
\subsection{Summary}
SMEML manages to return comparable accuracy results to its dumb couterpart while more than splitting the run time in half in the majority of benchmarks. Its performance is not limited by the size of the dataset, and it returned its first, third, and fourth best percentage-based run times on the 'large' dataset benchmarks (those exceeding 1000 rows). This is important in third world medicine where time is of the essence and there is a constant influx of new patient data. A practical demonsration of this software's real-world application can be found on our SmartDx website [18]. Source code can be found at [19].
\subsection{Limitations}
Our implementation of SMEML has limitations. These include a small training set due to lack of available datasets, finite computing power, time constraints, and a lack of access to paticular scientific literature. Our framework only improves on the model selection process and does not address the various other aspects of AutoML. Therefore, SMEML is not comparable to other full-featured AutoML frameworks.
\subsection{Future Work}
Future work will include increasing the size of the training set, implementing a fully fledged AutoML framework, and conducting a detailed experiment comparing SMEML to other popular AutoML frameworks. Furthermore, we will examine other types of machine learning such as regression and multiclass-classification.

@@

[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, 212, 106622 (2021), \url{https://doi.org/10.1016/j.knosys.2020.106622}.

[2] Nchasi, Goodluck, et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports, 5, 6 (2022), \url{https://doi.org/10.1002%2Fhsr2.893}.

[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 16 (2016), \url{}.

[4] Bajwa, Junaid, et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal, 8, 188-94 (2021), \url{https://doi.org/10.7861%2Ffhj.2021-0095}

[5] LeDell, E., and S. Poirier. “H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning, 2020, \url{www.automl.org/wp-content/uploads/2020/07/AutoML_2020_paper_61.pdf}.

[6] Olson, Randal S., 1, et al. "Automating Biomedical Data Science Through Tree-based Pipeline Optimization." Applications of Evolutionary Computation, 19, 123 (2016), \url{https://doi.org/10.1007/978-3-319-31204-0_9}.

[7] P\l{}o\'{n}ska, Aleksandra, et al. “MLJAR: State-of-the-art Automated Machine Learning Framework for Tabular Data.  Version 0.10.3.” MLJAR, (2021), \url{github.com/mljar/mljar-supervised}.

[8] Conrad, Felix, et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports, 12, 19350 (2022), \url{https://doi.org/10.1038/s41598-022-23327-1}.

[9] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." 4th MLSys Conference, (2021), \url{https://doi.org/10.48550/arXiv.1911.04706} .

[10] Ryzhkov, Alexander, et al. "LightAutoML: AutoML Solution for a Large Financial Services Ecosystem." arXiv, (2021), \url{https://doi.org/10.48550/arXiv.2109.01528}

[11] Akalin, Altuna. 3.3 Relationship Between Variables: Linear Models and Correlation | Computational Genomics With R. 30 Sept. 2020, \url{compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html}.

[12] Ms. Nancy Al Aswad. Lung Cancer. \url{www.kaggle.com/datasets/nancyalaswad90/lung-cancer}.

[13] Mansoor Iqbal. Chronic KIdney Disease Dataset. \url{www.kaggle.com/datasets/mansoordaku/ckdisease}.

[14] UCI Machine Learning. Pima Indians Diabetes Dataset. \url{https://www.kaggle.com/datasets/uciml/pima-indians-diabetes-database}.

[15] Izzet Turkalp Akbasli. Brain stroke prediction dataset. \url{https://www.kaggle.com/datasets/zzettrkalpakbal/full-filled-brain-stroke-dataset}.

[16] fedesoriano. Stroke Prediction Dataset. \url{www.kaggle.com/fedesoriano/stroke-prediction-dataset}.

[17] Rob Mulla. Eye State Classification EEG Dataset. \url{https://www.kaggle.com/datasets/robikscube/eye-state-classification-eeg-dataset}.

[18] SmartDx Website. \url{https://smartdx.vercel.app/}.

[19] Github Repository. \url{www.github.com/ericspring08/SMEML-Paper}.
}

>>>>

\author{%
  Eric Su Zhang$^1$ \\
  St. Mark's School of Texas\\
  10600 Preston Rd, Dallas, TX 75230\\
  \texttt{26zhange@smtexas.org} \\
  % examples of more authors
  \And
  Benjamin Joseph Michael Standefer$^2$ \\
  St. Mark's School of Texas \\
  10600 Preston Rd, Dallas, TX 75230 \\
  \texttt{26standeferb@smtexas.org} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\begin{abstract}
  Automated Machine Learning or AutoML has emerged as a popular field of research. We performed a literature review of existing AutoML papers and conducted a survey on five popular AutoML frameworks. Many of these frameworks optimize a form of model selection, but they all require every model to be run and evaluated. We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant. SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" brute-force framework, but in a fraction of the time. We also believe this innovation is particularly relevant to machine learning in healthcare because of the necessity for efficient diesease prediction. 
\end{abstract}

@@

Machine learning (ML) is a type of artificial intelligence (AI) that uses searching and trend-determining to make predictions. ML algorithms are trained and tested on a given dataset to become "smarter". Once they've learned the patterns typical of that data, they can make predictions based on similar data. These algorithms also require additional processes, however, like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning. This makes the process complex and time-inefficient. To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks [1].

One sector of the global industry that has the most potential for beneficial integration of AutoML frameworks is healthcare, particularly in developing countries. These countries have severe shortages of healthcare workers and limited tools for diagnosis. For example, Africa has 2.3 healthcare workers per 1000 individuals, while the Americas have 24.8 healthcare workers per 1000 [2]. The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030 [3]. Medical AIs typically automate repetitive tasks, making time consumption a primary concern [4]. This coupled with a lack of adequate resources makes designing faster diagnostic systems for developing countries' medical sectors a pivotal issue. 
%
Most AutoML frameworks implement some form of model selection where a pool of models are filtered until a final model is selected. However, these frameworks require that every model be run [1]. In theory, this means that much energy is spent training models that are unlikely to be selected. We propose SMEML, a novel model selection algorithm that automatically eliminates models that it believes will not be performant.

@@

\begin{table}
  \caption{Survey of Existing AutoML Frameworks}
  \label{automl-survey}
  \centering
  \begin{tabular}{lllllllll}
    \toprule
    Framework & EOU & M & FE & TM & HPT & Inter & Custom\\
    \midrule
    H2O AutoML [5] & Easy & 12 & Basic & Yes & Auto & SHAP & High\\
    TPOT [6] & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
    MLJAR [7,8] & Easy & 12 & Advanced & Yes & Auto & Basic & High\\
    FLAML [9] & Easy & 9 & Limited & Yes & Auto & SHAP & Low-Moderate\\
    LightAutoML [10] & Easy & 11 & Advanced & Yes & Auto & Basic & Moderate\\
    \bottomrule
  \end{tabular}
  \captionsetup{font=footnotesize}
  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, M: \# of models evaluated by framework, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
\end{table}
We systematically reviewed and compared five different AutoML frameworks, comparing every feature relevant to medical implementation. Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.

@@

Keeping the factors we have laid out in mind, we also uncovered a key continuity in framework design: frameworks must run the majority of their models to maximize accuracy at the expense of efficiency. Given the specific nature of certain tabular data, there are some models that are less likely to perform well, thus running and training these models is wasteful. Cutting these models completely, however, is not optimal, as they are the best option in a minority of cases. We hypothesized that using a combination of layered machine learning implementation and meta-feature extraction would yield an equally versatile system that minimizes time spent on training without sacrificing accuracy.

\section{Methodology}
When considering a specific dataset, the distribution, relationship between datapoints, and various other attributes can give us clues as to which models are likely to perform best. For example, linear models tend to work better on datasets where there is a linear relationship between features [11]. Accordingly, we can develop a boosting model to predict the best models based off extracted attributes from a dataset. These extracted attributes are shown in Table 2. Each attribute attempts to capture a specific type of relationship or distribution within the data.

We considered 28 different models, including all supervised and semi-supervised sklearn [12] classification models and common boosting models such as XGBoost [13], LightGBM [14], and Catboost [15].

To implement this model elimination process, we trained a boosting model on 268 kaggle datasets. We chose medical datasets and focused our approach on binary classification. We extracted the attributes in Table 2 from each dataset: this is the input for the boosting model. We then ran a "dumb" framework that trained every model on each dataset. The accuracy of every model is ranked, and every model is treated as a label with its value being its rank. Then we trained a multilabel regression to predict the rank of each model, giving the extracted attributes. We produced a median spearman correlation of 0.7301 between the predicted rank and the actual rank and a median p-value of 1.032e-05. Furthermore, we guarantee that we can predict a top two model within the predicted top eight 90.12\% of the time.

When a user inputs a dataset into SMEML, it first extracts the attributes from the dataset. It feeds these attributes into the boosting model to get the predicted rank of each model. Since we have determined that we can predict a top two model within the predicted top eight quite confidently, we can eliminate the bottom 20 models from the list. We run Bayseian optimization using scikit-optimize [16] on the top eight models to get the best hyperparamters for each model. We select the top models that have significantly better performance than other models. These models are stacked together to form the final model. This process is shown in Figure 1.
\begin{table}
  \caption{Attributes extracted from a dataset}
  \label{model-options-table}
  \centering
  \begin{tabular}{llll}
    \toprule
    Attribute & Formula & Purpose & Weight\\
    \midrule
    \# of Rows & $|\mathbf{A}|_r$ & DS & .0422 \\
    \hline
    \# of Columns & $|\mathbf{A}|_c$ & DS & .0415 \\
    \hline
    Target Distribution &
    $\frac{\max(\text{count}_1, \text{count}_0)}{|\mathbf{A}|_r}$
    & DT & .0489 \\
    \hline
    Numerical Columns &
    $\frac{|\mathbf{A}_{num}|}{|\mathbf{A}|_{c}}$
    & DT & .0428 \\
    \hline
    Binary Categorical Columns &
    $\frac{|\mathbf{A}_{bin}|}{|\mathbf{A}|_{c}}$
    & DT & .0117 \\
    \hline
    Mean \# of Distinct Values  & $\mu \left\{\text{\# of distinct values in column}\right\}$ & DT & .0076 \\ 
    \hline
    Mean IQR  & $\mu \left\{\text{IQR of column}\right\}$ & DD & .0594 \\ 
    \hline
    STD of IQR  & $\sigma \left\{\text{IQR of column}\right\}$ & DD & .0700 \\
    \hline
    Mean Q1 & $\mu \left\{\text{Q1 of column}\right\}$ & DD & .0789 \\
    \hline
    STD of Q1  & $\sigma \left\{\text{Q1 of column}\right\}$ & DD & .0613 \\
    \hline
    Mean Q3  & $\mu \left\{\text{Q3 of column}\right\}$ & DD & .0812 \\
    \hline
    STD of Q3  & $\sigma \left\{\text{Q3 of column}\right\}$ & DD & .1103 \\
    \hline
    Mean Percent of Z-Score Outliers  & 
    $\mu \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & ODP & .0558 \\
    \hline
    STD of Percent of Z-Score Outliers  &
    $\sigma \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & ODP & .0798 \\
    \hline
    Mean Correlation& $\mu \left\{\text{Correlation Matrix}\right\}$ & DL & .0559 \\
    \hline
    STD of Correlation & $\sigma \left\{\text{Correlation Matrix}\right\}$ & DL & .1526 \\
    \bottomrule
  \end{tabular}
  \captionsetup{font=footnotesize}
  \caption*{\textbf{Abbreviations}: DS: Data Size, DT: Data Type, DD: Data Distribution, ODP: Outlier Data Points, DL: Data Linearity, Weight: Variable Importance}
\end{table}

\begin {figure}
\centering
\includegraphics[width=\textwidth]{smeml-flowchart.png}
\caption{Illustration of the SMEML Process}
\end{figure}

@@

\subsection{Results}
\begin{table}
  \caption{Experiment Results}
  \label{model-options-table}
  \centering
  \begin{tabular}{llllll}
    \toprule
    % group 2, 3 as multicolumn and 4, 5 as multicolumn
    Dataset & \multicolumn{2}{c}{Accuracy} & \multicolumn{2}{c}{Time to Train (sec)} & Size (RxC)\\
    \cmidrule(lr){2-3} \cmidrule(lr){4-5}
    & SMEML & Dumb & SMEML & Dumb \\
    \midrule
    Lung Cancer Prediction [17] & .9839 & .9839 & 143.07 & 317.04 & 309x16\\
    Chronic Kidney Disease Dataset [18] & 1.0 & 1.0 & 419.64 & 788.46 & 400x26\\
    Pima Indians Diabetes Dataset [19] & .7857 & .8052 & 161.99 & 374.01 & 768x8 \\
    Brain Stroke Prediction Dataset [20] & .9458 & .9458 & 114.16 & 370.95 & 4892x11\\
    Stroke Prediction Dataset [21] & .9393 & .9393 & 172.67 & 385.23 & 5110x12 \\
    Eye State Classification [22] & .9536 & .9549 & 312.57 & 696.51 & 14980x15\\ 
    \bottomrule
  \end{tabular}
\end{table}

Several observations were made from running these datasets. First, accuracy did not change for 4 of the 6 benchmarks. The other two benchmarks on eye states and diabetes prediction represented a loss of accuracy for SMEML by 0.13\% and 1.95\%, respectively. Training time, however, favored SMEML in every trial. SMEML outperformed the dummy framework by 173.96 seconds in its worst performance on the lung cancer trial and by 383.94 seconds in its best performance on the eye state dataset. Relative to the dummy's performance, a percent decrease in time to run for SMEML of at least 46.78\% could be seen, with a decrease of up to 69.22\% observerd as well. SMEML's worst performance by percent decrease was also the performance in which it returned perfect accuracy. 
\section{Discussion}
\subsection{Summary}
SMEML manages to return comparable accuracy results to its dumb couterpart while more than splitting the run time in half in the majority of benchmarks. Its performance is not limited by the size of the dataset, and it returned its first, third, and fourth best percentage-based run times on the 'large' dataset benchmarks (those exceeding 1000 rows). This is important in third world medicine where time is of the essence and there is a constant influx of new patient data. A practical demonsration of this software's real-world application can be found on our SmartDx website [23]. Source code can be found at [24].
\subsection{Limitations}
Our implementation of SMEML has limitations. These include a small training set due to lack of available datasets, finite computing power, time constraints, and a lack of access to paticular scientific literature. Our framework only improves on the model selection process and does not address the various other aspects of AutoML. Therefore, SMEML is not comparable to other full-featured AutoML frameworks.
\subsection{Future Work}
Future work will include increasing the size of the training set, implementing a fully fledged AutoML framework, and conducting a detailed experiment comparing SMEML to other popular AutoML frameworks. Furthermore, we will examine other types of machine learning such as regression and multiclass-classification.

@@

[1] He, X., et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems. 212, 106622 (2021). \url{https://doi.org/10.1016/j.knosys.2020.106622}.

[2] Nchasi, G., et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports. 5, 6 (2022). \url{https://doi.org/10.1002/hsr2.893}.

[3] "Global Strategy on Human Resources for Health: Workforce 2030." World Health Organization. 16 (2020). \url{https://www.who.int/publications/i/item/9789241511131}.

[4] Bajwa, J., et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal. 8, 188-94 (2021). \url{https://doi.org/10.7861/fhj.2021-0095}.

[5] LeDell, E., and S. Poirier. “H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning. (2020). \url{https://automl.org/wp-content/uploads/2020/07/AutoML_2020_paper_61.pdf}.

[6] Olson, S., et al. "Automating Biomedical Data Science Through Tree-based Pipeline Optimization." Applications of Evolutionary Computation. 19, 123 (2016). \url{https://doi.org/10.1007/978-3-319-31204-0_9}.

[7] P\l{}o\'{n}ska, A., et al. “MLJAR: State-of-the-art Automated Machine Learning Framework for Tabular Data.  Version 0.10.3.” MLJAR. (2021). \url{https://github.com/mljar/mljar-supervised}.

[8] Conrad, F., et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports. 12, 19350 (2022). \url{https://doi.org/10.1038/s41598-022-23327-1}.

[9] Shang, Z., et al. "FLAML: A Fast and Lightweight AutoML Library." 4th MLSys Conference. (2021). \url{https://doi.org/10.48550/arXiv.1911.04706}.

[10] Ryzhkov, A., et al. "LightAutoML: AutoML Solution for a Large Financial Services Ecosystem." arXiv:2109.01528. (2021). \url{https://doi.org/10.48550/arXiv.2109.01528}.

[11] Akalin, A., "Computational Genomics With R." Chapman and Hall/CRC. 1, Section 3.3, (2020). \url{compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html}.

[12] Pedregosa, F., et al. "Scikit-learn: Machine Learning in Python." Journal of Machine Learning Research. 12, 2825 (2011). \url{https://doi.org/10.48550/arXiv.1201.0490}.

[13] Chen, T., et al. "XGBoost: A Scalable Tree Boosting System." 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining. (2016). \url{https://doi.org/10.1145/2939672.2939785}.

[14] Ke, G., et al. "LightGBM: A Highly Efficient Gradient Boosting Decision Tree." Advances in Neural Information Processing Systems. 30, 3149 (2017). \url{https://doi.org/10.48550/arXiv.1706.08359}.

[15] Prokhorenkova, L., et al. "CatBoost: Unbiased Boosting with Categorical Features." Advances in Neural Information Processing Systems. 32, 6639 (2018). \url{https://doi.org/10.48550/arXiv.1706.09516}.

[16] Head, T. et al. "Scikit-Optimize: Sequential Model-Based Optimization." Zenodo. (2020). \url{https://doi.org/10.5281/zenodo.1170575}.

[17] Ms. Nancy Al Aswad. Lung Cancer (dataset). \url{https://kaggle.com/datasets/nancyalaswad90/lung-cancer}.

[18] Mansoor Iqbal. Chronic KIdney Disease Dataset (dataset). \url{https://kaggle.com/datasets/mansoordaku/ckdisease}.

[19] UCI Machine Learning. Pima Indians Diabetes Dataset (dataset). \url{https://www.kaggle.com/datasets/uciml/pima-indians-diabetes-database}.

[20] Izzet Turkalp Akbasli. Brain stroke prediction dataset (dataset). \url{https://www.kaggle.com/datasets/zzettrkalpakbal/full-filled-brain-stroke-dataset}.

[21] fedesoriano. Stroke Prediction Dataset (dataset). \url{www.kaggle.com/fedesoriano/stroke-prediction-dataset}.

[22] Rob Mulla. Eye State Classification EEG Dataset (dataset). \url{https://www.kaggle.com/datasets/robikscube/eye-state-classification-eeg-dataset}.

[23] SmartDx Website. \url{https://smartdx.vercel.app/}.

[24] Github Repository. \url{https://github.com/ericspring08/SMEML-Paper}.
}
